---
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r footer-setup}
library(glue)
shiny_url <- "https://oferengel-posit.shinyapps.io/"

```


What's next?

`r emo::ji("ledger")` [Full list of tutorials supporting OpenIntro::Introduction to Modern Statistics](https://oferengel.github.io/ims-tutorials-4-umcg/)

`r emo::ji("spiral_notepad")` [Tutorial 1: Introduction to data](https://oferengel.github.io/ims-tutorials-4-umcg/01-data/)

`r emo::ji("one")` [Tutorial 1 - Lesson 1: Language of data](`r glue("{shiny_url}01-01-lesson/")`)

`r emo::ji("two")` [Tutorial 1 - Lesson 2: Types of studies](`r glue("{shiny_url}01-02-lesson/")`)

`r emo::ji("three")` [Tutorial 1 - Lesson 3: Sampling strategies and Experimental design](`r glue("{shiny_url}01-03-lesson/")`)

`r emo::ji("four")` [Tutorial 1 - Lesson 4: Case study](`r glue("{shiny_url}01-04-lesson/")`)

`r emo::ji("open_book")` [Learn more at Introduction to Modern Statistics](http://openintro-ims.netlify.app/)


## Submit

```{r encoder, echo=FALSE, context="server"}
encoder_logic()
```

```{r encode, echo=FALSE}
learnrhash::encoder_ui(ui_before = hash_encoder_ui)
```

