---
title: "Lab Name"
author: "Author Name"
date: "`r Sys.Date()`"
output: 
  html_document:
    highlight: "pygments"
    theme: "spacelab"
    toc: TRUE
    toc_float: TRUE
    code_folding: "show"
    df_print: paged
---

```{r setup, message=FALSE}
# 1. load the necessary libraries


# 2. use the read_csv file to read the dataset


```

### Exercise 1

**Question:**  How many observations are we missing weights from? How many are missing from the variable `physically_active_7d`?


```{r ex1-missing-data}
# Write your code to create determine the missing data

```

**Answer:** [Replace this with your answer]




### Exercise 2

**Question:**  Try to replicate the box-plot and the summary table shown below. What can you learn from it about the association between the variables `physical_3plus` and `weight`? What do you expect and why?


```{r ex2-descriptive}
# Insert code for Exercise 2 here


```

**Answer:** [Replace this with your answer]




### Exercise 3

**Question:** To test the difference between the two groups, we will run a t-test. Write the hypotheses for testing if the average weights are different for those who exercise at least times a week and those who don't. Run the t-test and formulate your conclusion by filling in the sentence shown below.

```{r ex3-t-test}
# Insert code for Exercise 3 here



```

**Answer:** [Replace this with your answer]




### Exercise 4

**Question:** Calculate the median and interquartile range for `arr_delay`s of flights in in the `sfo_feb_flights` data frame, grouped by carrier. Which carrier has the most variable arrival delays?

```{r ex4-ad-by-carrier}
# Insert code for the Exercise here


```


**Answer:** [Replace this with your answer]





### Exercise 5

**Question:** Create a list of `origin` airports and their rate of on-time-departure. Then visualize the distribution of  on-time-departure rate across the three airports using a segmented bar plot (see below). If you could select an airport based on on time departure percentage, which NYC airport would you choose to fly out of?
**Hint:** For the segmented bar plot, will need to map the `aes`thetic arguments as follows: `x = origin, fill = dep_type` and a `geom_bar()` layer. Create three plots, one with `geom_bar()` layer, one with `geom_bar(position = "fill")` and the third with `geom_bar(position = "dodge")`. Explain the difference between the three results.


```{r ex5-on_time_dep_rate}
# Insert code for the Exercise here


```



### Exercise 6

**Question:** Mutate the data frame so that it includes a new variable that contains the average speed, `avg_speed` traveled by the plane for each flight (in mph, or if you are brave, in km/h). Now make a scatter plot of `distance` vs. `avg_speed`. 
    Think carefully which of the two variables is the predictor (on the `x-axis`) and which is the outcome variable (on the `y-axis`) and explain why you made this choice. Describe the relationship between average speed and distance.

```{r ex6-avg-speed-distance}
# Insert code for the Exercise here


```

**Answer:** [Replace this with your answer]


### Exercise 7

**Question:** Replicate the following plot and determine what is the cutoff point for the latest departure delay where you can still have a chance to arrive at your destination on time. 

```{r ex7-plot-to-replicate}
# Insert code for the Exercise here


```

**Answer:** [Replace this with your answer]

