---
title: "Title of your work here"
author: "Your name(s) here"
output: html_document
---

In this tutorial, you will learn how to:

Practice using RMarkdown to create neat and reproducible reports
Load libraries into  the R environment so you can use them in your code chunks
Load a dataset and inspect it in the environment panel
Create a `table 1` of your dataset

## Practice using RMarkdown 

Change the YAML using the documentation for HTML features to include 

floating table of contents (toc)
paged table printing
a flatly theme (see section 3.1.4 in the documentation)

Use inline formatting to create

Hyperlinks. For example, you can find documentation to the use of HTML inline formatting here and here
Text written in Bold font
Third level section headers 
Unordered list items
Text marked as `inline code` using `backticks` 
The use of blockquotes 


Coding in R

The chunk below is our setup chunk. This is where we load our libraries (in this case, we are loading tidyverse and table1). We can also dataset our dataset from the file which you can find in a folder called "data". 

```{r setup, include=FALSE}
# Within a code chunk, hashtags function as comments
# Please remove the hashtags in the two lines below
# library(tidyverse)
# library(table1)


# Uncomment the line below
# load(file = "data/nhanes.Rdata")

```

Running the chunk above will introduce a dataset into your environment.  

The dataset is a random sample from the National Health and Nutrition Examination Survey (NHANES),  a survey designed to "assess the health and nutritional status of adults and children in the United States."

The variables in this dataset include:

sbp the systolic blood pressure
dbp  the diastolic blood pressure
age age in years
sex sex assigned at birth
income an indicator for the income class
smoker an indicator of participant's smoking status

Use chunk options to prevent the code from showing  in your final report.

Display the contents of the dataset by typing `nhanes` in the code chunk below

```{r display-nhanes}
# Write your code here

```

Generate a summary of the dataset (use the function `summary`)

```{r summary-nhanes}
# Use the summary function in this chunk

```

Use inline code to print out the total number of variables and the number of observed units in our dataset. 

**Answer:** The number of variables in our data-set is "r ncol(nhanes)" and the number of observed units is "r nrow(nhanes)"

## Create a "Table 1"

In most published articles, there is a "Table 1" containing descriptive statistics for the sample. This may include, for example, the mean and standard deviation for continuous variables, the frequency and proportion for categorical variables, and perhaps also the number of missing values.

The brute force method of creating such a table would be to compute each statistic for each variable of interest and then copy and paste the results into a table. But an easier way is to use the functions from the table1 package. Please use the documentation provided in this link to create the table below. 

```{r table-1}
# here the code for your table 1

```


## An extension

Extend the work by adding your own creative spin on what you've learned in this lab. For example, you can create a new table1 or count the number of distinct values of the income variable using the `count` function. You may add a new variable using the `mutate` function and display it in a table. 
Just be creative!

```{r extension}
# Write your code for the extension here

```


