---
title: "Lab Name"
author: "Author Name"
date: "`r Sys.Date()`"
output: 
  html_document:
    highlight: "pygments"
    theme: "spacelab"
    toc: TRUE
    toc_float: TRUE
    code_folding: "show"
    df_print: paged
---

```{r setup, message=FALSE}
# 1. load the library "tidyverse"
library(tidyverse)

# 2. use the read_csv file to read the dataset
nycflights <- read_csv("data/nycflights.csv")

```


### Exercise 1

**Question:**  Experiment with different binwidths to adjust your histogram in a way that will show its important features. You may also want to try using the `+ scale_x_log10()` . What features are revealed now that were obscured in the original histogram?


```{r ex1-hist-of-delays}
# Write your code to create a histogram of delays
ggplot(data = nycflights, aes(x = dep_delay)) + 
  geom_histogram(binwidth = .01) + 
  scale_x_log10(breaks=c(1:20, 50, 100, 500, 1000)) + 
  scale_y_log10()
```

**Answer:** Very skewed distribution suggests that delays are rare, but when there is a delay it could be very large. 



### Exercise 2

**Question:**  Create a new data frame that includes flights headed to SFO in February, and save this data frame as `sfo_feb_flights`.
How many flights meet these criteria?


```{r create-sfo_feb_flights}
# Insert code for Exercise 2 here
sfo_feb_flights <- nycflights %>%
  filter(dest == "SFO", month == 2)
```

**Answer:** the number of flights is `r nrow(sfo_feb_flights)`



### Exercise 3

**Question:** Describe the distribution of the **arrival** delays of flights headed to SFO in February, using an appropriate histogram and summary statistics.

```{r ex3-arrival-delay}
# Insert code for Exercise 3 here
ggplot(data = sfo_feb_flights, aes(x = arr_delay)) + 
  geom_histogram(binwidth = 5) 


ggplot(data = sfo_feb_flights, aes(x = arr_delay)) + 
  geom_histogram(binwidth = .1) + 
  scale_x_log10(breaks = c(1, 2, 3, 5, 10, 25, 50, 100))

sfo_feb_flights %>%
  summarise(mean_ad   = mean(arr_delay), 
            median_ad = median(arr_delay), 
            IQR_ad = IQR(arr_delay), 
            n         = n())

```



**Answer:** [Replace this with your answer]




### Exercise 4

**Question:** Calculate the median and interquartile range for `arr_delay`s of flights in in the `sfo_feb_flights` data frame, grouped by carrier. Which carrier(s) have the most variable arrival delays?

```{r ex4-ad-by-carrier}
# Insert code for the Exercise here
sfo_feb_flights %>%
  group_by(carrier) |> 
  summarise(mean_ad   = mean(arr_delay), 
            median_ad = median(arr_delay), 
            sd_ad = sd(arr_delay), 
            IQR_ad = IQR(arr_delay), 
            n         = n())


```


**Answer:** [Replace this with your answer]





### Exercise 5

**Question:** Create a list of `origin` airports and their rate of on-time-departure. Then visualize the distribution of  on-time-departure rate across the three airports using a segmented bar plot (see below). If you could select an airport based on on time departure percentage, which NYC airport would you choose to fly out of?
**Hint:** For the segmented bar plot, will need to map the `aes`thetic arguments as follows: `x = origin, fill = dep_type` and a `geom_bar()` layer. Create three plots, one with `geom_bar()` layer, one with `geom_bar(position = "fill")` and the third with `geom_bar(position = "dodge")`. Explain the difference between the three results.


```{r ex5-on_time_dep_rate}
# Insert code for the Exercise here
nycflights <- nycflights %>%
  mutate(dep_type = ifelse(dep_delay < 5, "on time", "delayed"))

nycflights %>%
  group_by(origin) %>%
  summarise(on_time_dep_rate = sum(dep_type == "on time") / n(), n = n()) %>%
  arrange(desc(on_time_dep_rate))  
 

nycflights |> 
  ggplot(aes(x = origin, fill = dep_type)) + geom_bar()


nycflights |> 
  ggplot(aes(x = origin, fill = dep_type)) + geom_bar(position = "fill")

nycflights |> 
  ggplot(aes(x = origin, fill = dep_type)) + geom_bar(position = "dodge")

```



### Exercise 6

**Question:** Mutate the data frame so that it includes a new variable that contains the average speed, `avg_speed` traveled by the plane for each flight (in mph, or if you are brave, in km/h). Now make a scatter plot of `distance` vs. `avg_speed`. 
    Think carefully which of the two variables is the predictor (on the `x-axis`) and which is the outcome variable (on the `y-axis`) and explain why you made this choice. Describe the relationship between average speed and distance.

```{r ex6-avg-speed-distance}
# Insert code for the Exercise here
nycflights |> 
  mutate(speed = distance / air_time) |> 
  ggplot(aes(distance, speed)) + 
  geom_point() 

```

**Answer:** [Replace this with your answer]


### Exercise 7

**Question:** Replicate the following plot and determine what is the cutoff point for the latest departure delay where you can still have a chance to arrive at your destination on time. 

```{r ex7-plot-to-replicate}
# Insert code for the Exercise here
nycflights %>%
  filter(carrier == "AA" | carrier == "DL" | carrier == "UA") |> 
ggplot(aes(x = dep_delay, y = arr_delay, color = carrier)) +
  geom_point(alpha = .5) 

```

**Answer:** [Replace this with your answer]
