---
title: "Lab Name"
author: "Author Name"
date: "`r Sys.Date()`"
output: 
  html_document:
    highlight: "pygments"
    theme: "spacelab"
    toc: TRUE
    toc_float: TRUE
    code_folding: "show"
    df_print: paged
---

```{r setup, message=FALSE}
# 1. load the library "tidyverse"
library(tidyverse)

# 2. use the read_csv file to read the dataset
nycflights <- read_csv("data/nycflights.csv")

```


### Exercise 1

**Question:**  Experiment with different binwidths and use the `+ scale_x_log10()` to adjust your histogram in a way that will show its important features. What features are revealed now that were obscured in the original histogram?


```{r ex1-hist-of-delays}
# Write your code to create a histogram of delays
ggplot(data = nycflights, aes(x = dep_delay)) + 
  geom_histogram(binwidth = .1) + 
  scale_x_log10()
```

**Answer:** [Replace this with your answer]



### Exercise 2

**Question:**  Create a new data frame that includes flights headed to SFO in February, and save this data frame as `sfo_feb_flights`.
How many flights meet these criteria?


```{r create-sfo_feb_flights}
# Insert code for Exercise 2 here
sfo_feb_flights <- nycflights %>%
  filter(dest == "SFO", month == 2)
```

**Answer:** the number of flights is `r nrow(sfo_feb_flights)`



### Exercise 3

**Question:** Describe the distribution of the **arrival** delays of then `sfo_feb_flights` using an appropriate histogram and summary statistics.

```{r ex3-arrival-delay}
# Insert code for Exercise 3 here
ggplot(data = sfo_feb_flights, aes(x = arr_delay)) + 
  geom_histogram(binwidth = .2) + 
  scale_x_log10(breaks = c(1, 2, 3, 5, 10, 25, 50, 100))

sfo_feb_flights %>%
  summarise(mean_ad   = mean(dep_delay), 
            median_ad = median(dep_delay), 
            IQR_ad = IQR(dep_delay), 
            n         = n())

```



**Answer:** [Replace this with your answer]



### Exercise 4

**Question:** Calculate the median and interquartile range for `arr_delay`s of flights in in the `sfo_feb_flights` data frame, grouped by carrier. Which carrier has the most variable arrival delays?

```{r ex4-arrival-delay-median-IQR}
# Insert code for the Exercise here


```


**Answer:** [Replace this with your answer]

