---
title: "Untitled"
author: "Ofer Engel"
date: "2023-11-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)  # For ggplot, dplyr, and friends
library(patchwork)  # For combining ggplot plots
library(GGally)     # For scatterplot matrices
library(broom)      # For converting model objects to data frames
# easystats::easystats_update()
library(easystats)
weather_atl <- read_csv("atl-weather-2019.csv")
```



```{r}
weather_atl_summer <- weather_atl %>% 
  filter(time >= "2019-05-01", time <= "2019-09-30") %>% 
  mutate(humidity_scaled = humidity * 100,
         moonPhase_scaled = moonPhase * 100,
         precipProbability_scaled = precipProbability * 100,
         cloudCover_scaled = cloudCover * 100)

model_complex <- weather_atl_summer |> 
  lm(
    temperatureHigh ~ humidity_scaled + 
      moonPhase_scaled + 
      precipProbability_scaled + 
      windSpeed + 
      pressure + 
      cloudCover_scaled, 
    data = _)

model_complex.ctr <- weather_atl_summer |> 
  mutate_if(is.numeric, scale) |>
  mutate_if(is.numeric, ~ .x / 2)  |> 
  lm(
    temperatureHigh ~ humidity_scaled + 
      moonPhase_scaled + 
      precipProbability_scaled + 
      windSpeed + 
      pressure + 
      cloudCover_scaled, 
    data = _)


p1 <- model_complex %>% 
  model_parameters() %>% 
  plot()

p2 <- model_complex.ctr %>% 
  model_parameters() %>% 
  plot()

p1 / p2

newdata_example <- tibble(
  humidity_scaled = 50, 
  moonPhase_scaled = 50,
  precipProbability_scaled = 50, 
  windSpeed = 1, 
  pressure = 1000, 
  cloudCover_scaled = 50
  )

tidy(model_complex, conf.int = TRUE) |> 
  bind_rows(tidy(model_complex.ctr, conf.int = TRUE) ) |> 
  arrange(term)

p1 <- tidy(model_complex, conf.int = TRUE) %>%
  filter(term != "(Intercept)") |> 
ggplot(aes(x = estimate, y = term)) +
  geom_vline(xintercept = 0, color = "red", linetype = "dotted") +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) + 
  labs(x = "Coefficient estimate", y = NULL) +
  theme_minimal()

p2 <- tidy(model_complex.ctr, conf.int = TRUE) %>%
  filter(term != "(Intercept)") |> 
  ggplot(aes(x = estimate, y = term)) +
  geom_vline(xintercept = 0, color = "red", linetype = "dotted") +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) + 
  labs(x = "Coefficient estimate", y = NULL) +
  theme_minimal()

library(patchwork)

p1 / p2

```



Marginal effects

I don’t have anything official, unfortunately. I have [this example](https://datavizf23.classes.andrewheiss.com/example/07-example.html#predicted-values-and-marginal-effects-in-2023) I use for teaching my dataviz class. 


```{r}
ggplot(weather_atl, aes(x = time, y = temperatureHigh)) +
  geom_line() +
  scale_y_continuous(
    sec.axis = sec_axis(
      trans = ~ (32 - .) * -5/9,
      name = "Celsius"
      )
    ) +
  labs(x = NULL, y = "Fahrenheit") +
  theme_minimal()
```


I have this [longer post](https://www.andrewheiss.com/blog/2022/05/20/marginalia/index.html#marginaleffectss-and-emmeanss-philosophies-of-averaging) going into more detail about the differences between all the different marginal estimands and their ordering and this about marginal vs. conditional effects - but those are all just written out examples, not anything like exercises or [activities](https://www.andrewheiss.com/blog/2022/11/29/conditional-marginal-marginaleffects/index.html)
