---
title: "Modelling Penguins"
author: "Ofer Engel"
output: 
  html_document:
    highlight: "pygments"
    theme: "spacelab"
    toc: TRUE
    toc_float: TRUE
    code_folding: "show"
    df_print: paged
---

```{r setup, message=FALSE}
# 1. load the appropriate libraries
library(tidyverse)
library(broom)
library(table1)
library(car)


# 2. use the read_rds file to read the dataset
penguins <- read_rds("data/penguins.rds")

```

### Exercise 1

**Question:**  1. Use the `table1` package to replicate the table below. Use the examples provided in the [following vignette](https://cran.r-project.org/web/packages/table1/vignettes/table1-examples.html).

```{r ex1-table1}
# Write your code to create a histogram of delays
table1(~body_mass_g + sex + island | species, penguins)
```

**Answer:** [Replace this with your answer]



### Exercise 2

**Question:**  Replicate the scatter plot below, coloring the  points according to the species. What can you tell about the relationship between bill depth and penguin weight? Comment on the intercepts and the slopes, associated with the three species (are they the same? similar? different).
Does the outcome variable appear normally distributed? Why does that matter?

```{r ex2-bodymass-billdepth}

penguins |> 
  ggplot(aes(bill_depth_mm, body_mass_g, color = species)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  theme_minimal()

```


**Answer:** [Replace this with your answer]


### Exercise 3 

**Question** Now replicate the plot below, describing the relationship between flipper length and body mass, and coloring the data according to the associated species. Facet the plot by island (search online if necessary). Finally, tell a story about the relationship between flipper length and weight in these three penguin species, and the distribution of penguins across the three islands.


```{r ex-3}

penguins |> 
  ggplot(aes(flipper_length_mm, body_mass_g, color = species)) + 
  geom_point() + 
  theme_minimal() + 
  facet_wrap(~island, nrow = 2)


```



